---
title: "Statistical Analysis With R"
author: "Madhu V"
date: "6/19/2019"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
always_allow_html: yes
urlcolor: blue    
---

```{r setup, include=FALSE}
# git config --global user.email "madhuvasudevan@yahoo.com"
# git config --global user.name "Madhu Vasudevan"

knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

# Getting Graphic

## Finding Patterns

```{r cars}
library(MASS)
Cars93

```

### Graphing a distribution
You can also embed plots, for example:

```{r price, echo=FALSE}
hist(Cars93$Price)
```

### Bar hopping 

```{r}
Cars93$Type
table(Cars93$Type)
barplot(table(Cars93$Type))
```

### Slicing the pie
```{r}
Cars93$Type
table(Cars93$Type)
pie(table(Cars93$Type))
```

### The plot of scatter  

```{r, fig.height = 20, fig.width = 5}
Cars93$Horsepower
Cars93$MPG.city
dotchart(Cars93$Horsepower, Cars93$Model)
```

### Of boxes and whiskers  

```{r}
boxplot(Cars93$Horsepower)
```

## Base R Graphics 

### Histograms 
```{r}
hist(Cars93$Price)
hist(Cars93$Price, 
     xlim = c(0,70), breaks = 4,
     xlab="Price (x $1,000)",
  main = "Prices of 93 Models of 1993 Cars")
```

### Adding graph features 

```{r}
hist(Cars93$Price, xlab="Price (x $1,000)", xlim = c(0,70),
  main = "Prices of 93 Models of 1993 Cars",probability
  = TRUE)
lines(density(Cars93$Price))
```

### Bar plots 
```{r}
Cars93[,"Type"]
table(Cars93$Type)
barplot(table(Cars93$Type))
barplot(table(Cars93$Type),ylim=c(0,25),
        axis.lty = "solid", space = .05,
        xlab="Type", ylab="Frequency")
```

### Pie graphs
```{r}
x <- table(Cars93$Type)
x
pie(table(Cars93$Type))
```

### Dot charts
```{r}
type.frame <- data.frame(table(Cars93$Type))
type.frame
dotchart(type.frame$Freq,type.frame$Var1)
dotchart(type.frame[,2],type.frame[,1])
```

### Bar plots revisited
```{r}
rev.values <-
c(1000,1300,1300,1100,1400,
  800,1200,1500,1850,2330,
  860,1300,1400,1600,1970,
  570,380,450,465,580,
  155,190,210,250,300)
space.rev <- matrix(rev.values,nrow=5,byrow = TRUE)
colnames(space.rev) <-
   c("1990","1991","1992","1993","1994")
rownames(space.rev) <- 
  c("Commercial Satellites Delivered",
  "Satellite Services",
  "Satellite Ground Equipment",
  "Commercial Launches",
  "Remote Sensing Data")
space.rev
color.names = c("black","grey25","grey50","grey75","white")
barplot(space.rev,
        xlab= "Year", ylab= "Revenue (X $1,000)", 
        col=color.names)
barplot(space.rev, beside = TRUE,
        xlab= "Year", ylab= "Revenue (X $1,000)", 
        col=color.names)
legend(1,2500,rownames(space.rev), cex=0.7, 
       fill = color.names, bty = "n")
```

### Barplot from dataframe?
```{r}
space.rev.df <- as.data.frame(space.rev)
barplot(as.matrix(space.rev.df), beside = TRUE,
        xlab= "Year", ylab= "Revenue (X $1,000)", 
        col=color.names)
legend(1,2500,rownames(space.rev.df), cex=0.7, 
       fill = color.names, bty = "n")
```

### Scatter plots
```{r}
plot(Cars93$Horsepower, Cars93$MPG.city,
  xlab="Horsepower",ylab="MPG City", main ="MPG City vs
  Horsepower")
```

Alternatively:
```{r}
plot(Cars93$MPG.city ~ Cars93$Horsepower,
   xlab="Horsepower",ylab="MPG City", main ="MPG City vs
   Horsepower")
```

### A plot twist 
```{r}
plot(Cars93$Horsepower,Cars93$MPG.city, xlab="Horsepower",
   ylab="MPG City", main = "MPG City vs Horsepower",pch=16)
```

```{r}
str(Cars93$Cylinders)
as.character((Cars93$Cylinders))
plot(Cars93$Horsepower,Cars93$MPG.city, xlab="Horsepower",
   ylab="MPG City", main = "MPG City vs Horsepower", pch
   = as.character(Cars93$Cylinders))
```

### Scatter plot matrix
```{r}
cars.subset <- subset(Cars93, 
      select = c(MPG.city,Price,Horsepower))
head(cars.subset)
pairs(cars.subset)
```

Adding 'Cylinders' variable to the mix
```{r}
cars.subset2 <- subset(Cars93, 
      select = c(MPG.city,Price,Horsepower,Cylinders))
head(cars.subset2)
pairs(cars.subset2)
```

### Box plots
```{r}
boxplot(Cars93$Horsepower ~ Cars93$Cylinders, xlab="Cylinders",
   ylab="Horsepower")

```

Alternatively
```{r}
boxplot(Horsepower ~ Cylinders, data = Cars93,
xlab="Cylinders", ylab="Horsepower")
```

Alternatively:
```{r}
plot(Horsepower ~ Cylinders, data = Cars93,
xlab="Cylinders", ylab="Horsepower")
```



